Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
minor fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60906 72bbbca6-d526-0410-a7d9-f06f51895060

Kazakh (қазақ тілі), a Turkic language of Central Asia, is spoken by around 13 million people in Kazakhstan, China, Mongolia, and adjacent areas \parencite{ethnologue}.  While works like \textcite{Balaqayev54} provide decent syntactic overviews of the language, there is little to no work on the syntax of Kazakh within modern theoretical syntactic frameworks.  The authors are familiar with work on related languages, such as Turkish (e.g., \cite{Kornfilt97} and \cite{GokselKerslake05}); while not directly consulted in this work, such work has contributed to our understanding of Kazakh syntax.

>>>>

Kazakh (қазақ тілі), a Turkic language of Central Asia, is spoken by around 13 million people in Kazakhstan, China, Mongolia, and adjacent areas \parencite{ethnologue}.  While works like \textcite{Balaqayev54} provide decent syntactic overviews of the language, there is little to no work on the syntax of Kazakh within modern theoretical syntactic frameworks.  The authors are familiar with such work on related languages, such as Turkish (e.g., \cite{Kornfilt97} and \cite{GokselKerslake05}); while not directly consulted for this work, these works have contributed to our understanding of Kazakh syntax.
